A large-scale study of polymorphism

### 2019-03-15 paper/main.tex
minor

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\usepackage{booktabs} % For formal tables

\usepackage{listings}
\lstset{language=R}

% Style Stuff
\usepackage{my_style}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA}
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}

\acmSubmissionID{123-A12-B3}

\begin{document}
\title{How R R's Types Used}
% \titlenote{Produces the permission block, and
%   copyright information}
\subtitle{A Study of Type Usage in R}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

\author{Alexi Turcotte}
\authornote{Work of this author was partially supported by NSERC.}
% \orcid{1234-5678-9012}
\affiliation{%
  \institution{Northeastern University}
%   \streetaddress{P.O. Box 1212}
%   \city{Dublin}
%   \state{Ohio}
%   \postcode{43017-6221}
}
\email{alexi@ccs.neu.edu}

% if the default list of authors is too long for headers:
% \renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}

\end{abstract}

@@

I set up author notes:
\KS{for Konrad}, \JV{for Jan}, and \AT{for myself}.
Just do backslash and your initials (see source).

@@

%
%
%
%
%
%
\section{Introduction}

@@

%
%
%
%
%
%
\section{Conclusions and Future Work}

>>>>

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{booktabs} % For formal tables
\usepackage{listings}
\lstset{language=R}
\usepackage{my_style}

\setcopyright{none}
%\setcopyright{acmcopyright}%\setcopyright{acmlicensed}
%\acmDOI{10.475/123_4}
%\acmISBN{123-4567-24-567/08/06}
%\acmConference[OOPSLAs]{Woodstock conference}{July 1997}{El Paso, Texas USA}
%\acmYear{1997}%\copyrightyear{2016}%\acmPrice{15.00}
\begin{document}

\title{A large-scale study of polymorphism}

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language is geared towards exploratory
data

The R programming language is widely used in a variety of scientific domains
for tasks related to data analysis. Over the last two decades many libraries
have been developed to facilitate all steps of the data analysis process.
These libraries are stored in the CRAN reposot
\end{abstract}

@@

@@

%
\section{Introduction}

@@

\section{Conclusions and Future Work}
